Quantum Hoare Type Theory

### 2020-11-13 ms-paper/ms-paper.tex
Revise projections and their appearance

\lstset{
	basicstyle=\small\ttfamily,
	flexiblecolumns=false,
	basewidth={0.5em,0.45em},
	commentstyle=\color{dkgreen},
	keywordstyle=\bfseries\color{blue},
	stringstyle=\color{violet},
	literate={+}{{$+$}}1 {/}{{$/$}}1 {*}{{$*$}}1 {=}{{$=$}}1
	{√}{{$\surd$}}1
	{>}{{$>$}}1 {<}{{$<$}}1 {λ}{{$\lambda$}}1
	{\\\\}{{\char`\\\char`\\}}1
	{⇐}{{$\Leftarrow$}}1 {⇒}{{$\Rightarrow$}}2
	{\ .}{{$\circ$}}2 {\ .\ }{{$\circ$}}2
	{|}{{$\vert$}}1 {⟩}{{$\rangle$}}1
	{∧}{{$\wedge$}}1 {∨}{{$\vee$}}1
	{∈}{{$\in$}}1 {Π}{{$\Pi$}}1
	{⊗}{{$\otimes$}}1
	{⊤}{{$\top$}}1
	{=q}{{$=_q$}}2 {=c}{{$=_c$}}2
	{α}{{$\alpha$}}1 {β}{{$\beta$}}1
}

@@

\begin{itemize}
	\item $\top$ represents the complete Hilbert space, $\mathcal{H}$, under consideration.
	\item $\bot$ represents the zero-dimension subspace of Hilbert space, $\{0\}$.
	\item $X \wedge Y$ is taken to be the set intersection of the two subspaces: $X \cap Y$.
	\item $X \vee Y$ is modeled as the sum (linear combination) of the subspaces $X$ and $Y$. In other words, it is the closed subspace of the union of the two subspaces: $\overline{\mathit{span}(X \cup Y)}$, where $\overline{X}$ denotes that $X$ is a closed subspace.
	\item $X^\bot$ denotes the orthocomplement of $X$ which includes all vectors in $\mathcal{H}$ that are orthogonal to $X$.
\end{itemize}

@@

>>>>

\lstset{
	basicstyle=\small\ttfamily,
	flexiblecolumns=false,
	basewidth={0.5em,0.45em},
	commentstyle=\color{dkgreen},
	keywordstyle=\bfseries\color{blue},
	stringstyle=\color{violet},
	literate={+}{{$+$}}1 {/}{{$/$}}1 {*}{{$*$}}1 {=}{{$=$}}1
	{√}{{$\surd$}}1
	{>}{{$>$}}1 {<}{{$<$}}1 {λ}{{$\lambda$}}1
	{\\\\}{{\char`\\\char`\\}}1
	{⇐}{{$\Leftarrow$}}1 {⇒}{{$\Rightarrow$}}2
	{\ .}{{$\circ$}}2 {\ .\ }{{$\circ$}}2
	{|}{{$\vert$}}1 {⟩}{{$\rangle$}}1
	{∧}{{$\wedge$}}1 {∨}{{$\vee$}}1
	{∈}{{$\in$}}1 {Π}{{$\Pi$}}1 {∃}{{$\exists$}}1
	{⊗}{{$\otimes$}}1 {⊕}{{$\oplus$}}1
	{⊤}{{$\top$}}1
	{=q}{{$=_q$}}2 {=c}{{$=_c$}}2
	{α}{{$\alpha$}}1 {β}{{$\beta$}}1
	{_i}{{$_i$}}1
	{\ .\ }{{$\cdot$}}1
}

@@

\begin{itemize}
	\item $\top$ represents the complete Hilbert space, $\mathcal{H}$, under consideration.
	\item $\bot$ represents the zero-dimension subspace of Hilbert space, $\{0\}$.
	\item $X \wedge Y$ is taken to be the set intersection of the two subspaces: $X \cap Y$.
	\item $X \vee Y$ is modeled as the sum (linear combination) of the subspaces $X$ and $Y$. In other words, it is the closed subspace of the union of the two subspaces: $\overline{\mathit{span}(X \cup Y)}$, where $\overline{X}$ denotes the closure of $X$.
	\item $X^\bot$ denotes the orthocomplement of $X$ which includes all vectors in $\mathcal{H}$ that are orthogonal to $X$.
\end{itemize}

@@

\section{Other examples}

\subsection{QPL}

\lstinputlisting[language=QHaskell]{qpl.qh}

\subsection{Quantum Lambda Calculus}
\lstinputlisting[language=QHaskell]{qlc.qh}

\subsection{QWire Core}
\lstinputlisting[language=QHaskell]{paykin.qh}
